Binary- and integer linear programming can be used to model a wide range of problems by posting linear constraints and 
using and a linear objective function. A integer linear program (ILP) can be writing on the form: 
\begin{align}
 \text{Minimize }\; &z =  \mathbf{c}^T\mathbf{x} \\ 
 \text{subject to } \; & A\mathbf{x} \leq \mathbf{b} \\ 
 & \mathbf{x} \in \mathbb{Z}^n
\end{align}
Here $A$ is a $n \times m$ matrix of coefficients, $\mathbf{b} \in \mathbb{R}^m$, $z$ is the value of the objective 
function and $\mathbf{c} \in \mathbb{R}^n$. The first line is the objective function and can easily be transformed to a 
maximization problem by multiplying by $-1$. The relation in line 2 can be a mix of $\{\leq,=,\geq\}$ but greater 
than or equal can be transformed to less than or equal by multiplying both side of the constraint by $-1$.  \\ 
A candidate solution is an assignment of values to all variables $\mathbf{x}$ and a solution is said to be feasible if 
all constraints are satisfied. The set of feasible solutions consist of integer point in a $n$ dimensional space and 
the point that minimize the objective function is said to be the optimal solution. There can be multiple optimal 
solutions for a given model. \\
Solving a general integer program or binary program is a NP-hard problem \cite[p.30]{ilpbog} and several techniques are 
developed for solving them. The techniques can be i.e. branch and bound, cutting plane and branch and cut 
\cite[p.31]{ilpbog}. An integer linear program can be relaxed by relaxing the integer constraint, line 3 changed to 
$\mathbf{x} \in \mathbb{R}^n$, on the variables creating a linear programming problem \cite[p. 30]{ilpbog}. The linear 
programming problem is easier to solver than the integer programming problem and can be used to find bounds on the 
integer programming problem. The linear formulation can be transformed to \emph{standard form}, all constraints are 
equality constraints, by introducing auxiliary variables and then solved using the simplex method. \\ 
There exist several solver for (integer) linear programming problems such as Cplex, Gurobi, GLPK and Scip. 