There are different ways of measuring the quality of an solution. For a CSP a feasible solution needs to be found but 
different feasible solutions are equally good.  \\
In a COP the feasible solutions are compared by an objective function that gives the feasible solution a measurement 
of quality. \\ 
There are different ways of differentiating infeasible solution from other solutions, feasible or infeasible. The 
evaluation function is a combination of the objective function and the violated constraints. \\ 
Each constraint can be given a weight and together with the violation degree it contribute to the evaluation function. 
I.e. a constraint has weight ten and a violation degree of three it then contribute $3\cdot 10 = 30$ to the evaluation 
function. In this way the search priorities to satisfy certain constraints more than other. This method can have the 
negative effect that it might priorities to have all constraint with violation degree close to zero instead of 
one constraint with very high violation degree. If many constraint are violated it might take more iterations to get to 
feasible solution than if only a single constraint is infeasible. \\ 
Another way it to use a priority for each constraint as a lexicographic ordering, and try to satisfy constraints in 
that order. Once a group of constraints with priority $p$ is feasible they are always kept feasible and it tries to 
satisfy constraint of priority $p-1$. This will reduce the search space each time a group of constraints is satisfied 
and might lead to a scenario where the optimal solution cannot be reached. \\ 
This framework introduce a third way that uses priorities of constraints for a lexicographic ordering. Instead of 
evaluation a single value a vector of values from each solution can be compared in lexicographic order. The values 
representing violations of constraints of priority $p$ is first compared if equal it moves to $p-1$ and so on. The 
first vector to have a smaller value is considered the best. This prevent getting trapped in a subset of the search 
space S. \\ 
The vectors are never compared implementation wise but the delta evaluation function returns a delta vector 
that is used for evaluation instead of a delta value. This will be discussed further in section \ref{sec_local}.