Constraint programming involves defining variables and constraints like ILP but often a wide range of constraints can 
be used. Constraint programming is declarative programming that is the program describe the desired result 
and not the commands or steps to reach it, just like ILP. Constraint programming uses some interface either a 
programming language or a framework that have procedures implement to solve the problem according to the constraints 
posted. The language or framework may provides global constraint that can be used to formulate the problem. An example 
of a global constraint is the {\sffamily{alldifferent(\textbf{x})}} constraint that specify the variables \textbf{x} 
must have pairwise distinct values.  \\ 
Two important aspects of solving a CSP are inference and search. \emph{Inference} is adding constraints to the CSP that 
does not eliminate any feasible solution but might make it easier to solve the CSP \cite[p.301]{CPbog}. 
Local constraint propagation is an example of inference when dealing with variables with finite domain and can be used 
to eliminate large subspaces of the search space $S$. Propagation can be restricting domains of variables, called 
filtering, or combinations of values to variables, based on the constraint doing propagation \cite[p. 169]{CPbog}. 
Propagation can be done when a constraint is created by eliminating values from the domain of variables. I.e. by 
doing propagation on the constraint $x_1 + x_2 \leq 2$ where $x_1,x_2 \in \mathbf{Z}^+$ we can reduce the domain of the 
variables to $\{0,1,2\}$. If we set $x_1 =1$ we can again do propagation and reduce the domain of $x_2$ to $\{0,1\}$. 
\\ 
Search strategies explores possible assignments of variables and an exhaustive search would be a combination of all 
possible assignments of values to the variables. When combining propagation and search strategies the search space can 
be examined exhaustively and large subspaces can be pruned by propagation. \\ 
COP