Metaheuristics defines how the search space should be explored in where as local search algorithms that focus more on 
the neighborhood of the solution. Iterative improvement is often fast to find a local optimum depending on the size of 
the neighborhood. Usually only a small fraction of local optima are close to optimality and they can be a poor quality 
solution \cite[p.135]{lsbog}. Metaheuristics are used to get out of local optima to search different parts of the 
search space. \\
One of the simple Metaheuristics is \emph{iterative local search} that remembers the best solution 
found so far and uses two local search algorithms, random walk and iterative improvement. It uses iterative improvement 
to find a local optima and compare it to the best solution so far. Then uses random walk for some iterations to escape 
the local optima. These two algorithms are repeated until the termination criteria is reached. \\ 
Another metaheuristics is \emph{tabu search} that implements an iterative improvement with a modified best improvement 
pivoting rule. It chooses the neighborhood operation that will leads to the best solution in the neighborhood but not 
necessarily an improving solution. In addition to the modification of the pivot rule it implements a tabu list $T$ that 
keeps track of the last $t$ solution. The solution in the tabu list are not consider when looking for the next 
solution. It might be very memory expensive to keep track of the last $t$ solutions. An alternative way of implementing 
the tabu list is to keep track of the last $t$ neighborhood operations and forbid the reverse neighborhood operation. 
This is more restrictive since the reverse neighborhood operations might not lead to a solution visited within 
the last $t$ iterations. To compensate for this a \emph{aspiration criteria} can be implemented. Aspiration criteria is 
a set of rules that can overrule the tabu list \cite[p.139-140]{lsbog}. A common aspiration criteria is to ignore the 
tabulist if the neighborhood operation leads to the best solution found so far. \\
Several other metaheuristics exist such as variable neighborhood search and very large scale neighborhood search. 
Variable neighborhood search uses different neighborhood functions, hence different neighborhoods. Very large scale 
neighborhood search changes many variable in each neighborhood operation which give a very large neighborhood but might 
need fewer iteration to find a good quality solution. 