Simple problem will be modeled in this section and the different parts of this constraint based local search solver 
will be illustrated. \\
\boste{New subsection- The problem} \\ 
A city have budget of 50 million kr. for a festival and have some suggested activities. The activities have 
an individual cost and have been given a score based on how successful the activity is expected to be. The duration of 
the festival is three weeks and the activities have individual requirement to which week the can be planned. Exactly 
two must be planned the first week, at most two the second week and at most one the third week. The job is to 
plan activities with in the budget and schedule maximizing the score. Table \ref{tab_activity} shows the data given. \\
\begin{table}[b]
\centering
\begin{tabular}{|l|l|l|l|l|l|}
\hline
Activity No. & Cost & Score & Week 1 & Week 2 & Week 3 \\ \hline
1            & 20   & 3     & yes    & yes    & no     \\ \hline
2            & 10   & 2     & yes    & no     & no     \\ \hline
3            & 35   & 4     & no     & no     & yes    \\ \hline
4            & 42   & 5     & yes    & yes    & yes    \\ \hline
5            & 13   & 2     & no     & yes    & no     \\ \hline
6            & 37   & 4     & yes    & no     & yes    \\ \hline
\end{tabular}
\caption{Suggested activities}
\label{tab_activity}
\end{table} \noindent
If an activity is chosen it is chosen for all the weeks with yes. \\ 
\boste{Section - Model}
Each of the activities can be represented by a binary variable whether the activity is chosen or not. The constraint of 
each week can be modeled with the \class{Linear} constraint \boste{Somewhere I should describe the constraints and 
invariants implemented}. 